Model LF

### 2022-10-29 Final test.Rmd
Nu med participation kanal

COMMENT> 
IDENTITY> lf
EQ> lf = (part*pop)/1000
IF> shock_part_model <=0
IDENTITY> lf
EQ> lf = (part1*pop*(1-old_age_ratio))/1000
IF> shock_part_model > 0
IDENTITY> lf
EQ> lf = lf_test
IF> shock_lf_model > 0

@@

```{r}
###Gengivelse af stød til model
part_bs1 = Shock_bs1$simulation$part
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs2 = Shock_bs2$simulation$komp_r
part_bs2 = Shock_bs2$simulation$part
yk_ds_bs2 = Shock_bs2$simulation$yk_ds
pc_ds_bs2 = Shock_bs2$simulation$pc_ds
wage_ds_t_bs2 = Shock_bs2$simulation$wage_ds_t
ur_ds_bs2 = Shock_bs2$simulation$ur_ds
emp_bs2 = Shock_bs2$simulation$emp
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
pconk_ds_bs2= Shock_bs2$simulation$pconk_ds
tilpas_pr_bs2 = Shock_bs2$simulation$tilpas_pr
u_ds_bs2 = Shock_bs2$simulation$u_ds
part_bs2 = Shock_bs2$simulation$part
nben_h_bs2 = Shock_bs2$simulation$nben_h
wage_ds_bs2 = Shock_bs2$simulation$wage_ds
dp_person_bs2 = Shock_bs2$simulation$dp_person
kont_h_ratio_bs2 = Shock_bs2$simulation$kont_h_ratio
unemp_bs2 = Shock_bs2$simulation$unemp
nl_g_bs2 = Shock_bs2$simulation$nl_g
inflation_bs2 = Shock_bs2$simulation$inflation

@@

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

```{r}
###Gengivelse af stød til model
part_000 = Shock_0$simulation$part
unemp_000 = Shock_0$simulation$unemp
komp_r_01 = Shock_0$simulation$komp_r
part_01 = Shock_0$simulation$part
yk_ds_01 = Shock_0$simulation$yk_ds
pc_ds_01 = Shock_0$simulation$pc_ds
wage_ds_t_01 = Shock_0$simulation$wage_ds_t
ur_ds_01 = Shock_0$simulation$ur_ds
emp_01 = Shock_0$simulation$emp
yd_hk_ds_01 = Shock_0$simulation$yd_hk_ds

@@

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

yk_ds_07 = Shock_7$simulation$yk_ds
emp_07 = Shock_7$simulation$emp
wage_ds_07= Shock_7$simulation$wage_ds
ur_ds_07 = Shock_7$simulation$ur_ds
pc_ds_07 = Shock_7$simulation$pc_ds
yd_hk_ds_07 = Shock_7$simulation$yd_hk_ds
pconk_ds_07 = Shock_7$simulation$pconk_ds
komp_r_07 = Shock_7$simulation$komp_r
max_dp_07 = Shock_7$simulation$max_dp
nben_h_07 = Shock_7$simulation$nben_h
yd_hk_ds_07 = Shock_7$simulation$yd_hk_ds
ik_07 = Shock_7$simulation$ik
wage_ds_t_07 = Shock_7$simulation$wage_ds_t
nben_h_un_07 = Shock_7$simulation$nben_h_un
nl_g_07 = Shock_7$simulation$nl_g
nsben_h_07 = Shock_7$simulation$nsben_h
dp_person_07 = Shock_7$simulation$dp_person
u_ds_07 = Shock_7$simulation$u_ds
shock_kuld_07 = Shock_7$simulation$shock_kuld
unemp_07 = Shock_7$simulation$unemp
```

```{r}
plot(((emp_07 - emp_bs7)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment", ylim= c(-350, 300));
lines(((emp_04 - emp_bs4)*1000), col= "black");
lines(((emp_02 - emp_bs2)*1000), col= "red");
lines(((emp_01 - emp_00)*1000), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

@@

>>>>

COMMENT> 
IDENTITY> lf
EQ> lf = (part*pop)/1000
IF> shock_part_model <=0
IDENTITY> lf
EQ> lf = (part1*pop*(1-old_age_ratio))/1000
IF> shock_part_model > 0
IDENTITY> lf
EQ> lf = lf_test1
IF> shock_lf_model > 0

@@

```{r}
###Gengivelse af stød til model
part_bs1 = Shock_bs1$simulation$part
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_ds_bs1 = Shock_bs1$simulation$yk_ds
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation

yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prod_bs1 = Shock_bs1$simulation$prod

xk_ds_bs1 = Shock_bs1$simulation$xk_ds
mk_ds_bs1 = Shock_bs1$simulation$mk_ds

net_balance_bs1 = xk_ds_bs1 - mk_ds_bs1
net_balance_bs1_ratio= (xk_ds_bs1 - mk_ds_bs1)/yk_ds_bs1

ik_bs1 = Shock_bs1$simulation$ik
mk_bs1 = Shock_bs1$simulation$mk

ik_ratio_bs1 = ik_bs1/yk_ds_bs1
mk_ratio_bs1 = mk_bs1/yk_ds_bs1

c_ratio_bs1 = pconk_ds_bs1/yk_ds_bs1
```

@@

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

```{r}
###Gengivelse af stød til model
part_000 = Shock_0$simulation$part
unemp_000 = Shock_0$simulation$unemp
komp_r_000 = Shock_0$simulation$komp_r
part_000 = Shock_0$simulation$part
yk_ds_000 = Shock_0$simulation$yk_ds
pc_ds_000 = Shock_0$simulation$pc_ds
wage_ds_t_000 = Shock_0$simulation$wage_ds_t
ur_ds_000 = Shock_0$simulation$ur_ds
emp_000 = Shock_0$simulation$emp
yd_hk_ds_000 = Shock_0$simulation$yd_hk_ds

tilpas_pr_000 = Shock_0$simulation$tilpas_pr
u_ds_000 = Shock_0$simulation$u_ds
part_000 = Shock_0$simulation$part
nben_h_000 = Shock_0$simulation$nben_h
wage_ds_000 = Shock_0$simulation$wage_ds
dp_person_000 = Shock_0$simulation$dp_person
kont_h_ratio_000 = Shock_0$simulation$kont_h_ratio

nl_g_000 = Shock_0$simulation$nl_g

yd_hk_ds_000 = Shock_0$simulation$yd_hk_ds
wage_gap1_000 = Shock_0$simulation$wage_gap1
wage_gap_000 = Shock_0$simulation$wage_gap
prod_000 = Shock_0$simulation$prod
```

@@

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

yk_ds_07 = Shock_7$simulation$yk_ds
emp_07 = Shock_7$simulation$emp
wage_ds_07= Shock_7$simulation$wage_ds
ur_ds_07 = Shock_7$simulation$ur_ds
pc_ds_07 = Shock_7$simulation$pc_ds
yd_hk_ds_07 = Shock_7$simulation$yd_hk_ds
pconk_ds_07 = Shock_7$simulation$pconk_ds
komp_r_07 = Shock_7$simulation$komp_r
max_dp_07 = Shock_7$simulation$max_dp
nben_h_07 = Shock_7$simulation$nben_h
yd_hk_ds_07 = Shock_7$simulation$yd_hk_ds
ik_07 = Shock_7$simulation$ik
wage_ds_t_07 = Shock_7$simulation$wage_ds_t
nben_h_un_07 = Shock_7$simulation$nben_h_un
nl_g_07 = Shock_7$simulation$nl_g
nsben_h_07 = Shock_7$simulation$nsben_h
dp_person_07 = Shock_7$simulation$dp_person
u_ds_07 = Shock_7$simulation$u_ds
shock_kuld_07 = Shock_7$simulation$shock_kuld
unemp_07 = Shock_7$simulation$unemp

part_07 = Shock_7$simulation$part
```

```{r}
plot(((emp_07 - emp_bs7)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment", ylim= c(-5000, 300));
lines(((emp_04 - emp_bs4)*1000), col= "black");
lines(((emp_02 - emp_bs2)*1000), col= "red");
lines(((emp_01 - emp_00)*1000), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

@@

```{r}
plot(part_07, col= "red"); lines(part_bs7, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```
